Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-20 paper.tex
Important concern to justify the paper
Have a look @JJ @pacastillo @7ossam81
SotA revised

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
An important task when publishing a new book is determining an accurate number 
of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
We evaluate our approach on the real data collected by a Spanish publishing company.
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

Sales prediction is an important problem that can improve the quality of business 
strategy for different companies. 
Traditionally, sales prediction problems have been solved using advaced methods 
such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, 
fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.

The most used technique to tackle sales forecasting problems is time-series prediction methods
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10},
however the correctness of the problem data strongly affects the predictions obtained.
Moreover, this kind of methods are based on using historical data to make time series.
However, in the case of new products sales prediction (such as the issue of new books), 
there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale.

Not only the lack of historical data makes this a complex problem, but also the fact 
that several variables (seasonality, promotions, or fashions) might influence predictions
\cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as
data clustering and fuzzy neural networks \cite{Chang2009}  or
extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this sense, several authors have proposed using ensemble of models for sales forecasting, 
as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
empirical model decomposition and extreme learning machine to develop an effective 
forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
for better handling of seasonal changes and fluctuations in consumer demands,
while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
and artificial neural network for sales forecasting in printed circuit board industry.
Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
a forecasting method based on extreme machine learning with adaptive metrics 
of inputs \cite{Xia2012}.
Ching et al. \cite{ChingChin2010} use a decision-support system to classify new 
products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
that products in the same class would follow a similar sales pattern. 
In any case, the proposed system can not deal with qualitative 
data related to the products.

Finally, in those problems where historical data are available, authors have 
proposed applying classical time series forecasting methods.
In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
to forecast the future sales of a printed circuit board is proposed.
Recent works propose take advantage of information extracted from online reviews, 
such as in \cite{ChernWSF15} where an analysis on historical data throughout online 
reviews, reviewer characteristics, and review influences to understand how 
electronic `word-of-mouth' influences product sales is presented.
Similar works propose take advantage of information published on specialized 
blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, having confirmed relationships between 
the number of blog references and book sales, at the time that different sales 
patterns have been observed by analysing books in series (the first book published 
takes the longest period to achieve every single sales scale, while the second book 
takes the second longest period, and so on).
In these cases, sales forecasting problems can be carried out thanks to a big 
amount of online reviews and historical data.

This paper continues our work on the prediction of sales of a new product for 
which no historical data are available, and where the classical forecasting methods 
based on time-series are not adequate.
In this sense, in \cite{Castillo2016books} the main factors influencing sales where 
analyzed in order to create a tool, based on several regression methods, that the 
publisher can use to decide how many books should be printed.

In this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
% TODO: complete this paragraph.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining an accurate number 
of copies to be printed. Doing both an under- or an overestimation will lead to financial losses.
In this paper, we address the problem of predicting total sales using cost-sensitive ensemble methods.
% Antonio - explain briefly what are them
These can be used as reliable decision-aid tools for publishers, as a part of the final stages of the editorial process. 
Thus, a real dataset including the complete sales data for books published in Spain across several years has been used to compute the prediction models.
% Antonio - extend a bit this with the followed methodology.
% Explain also the method you are using and why it's an improvement
% over the previous one - JJ
We evaluate our approach on the real data collected by a Spanish publishing company.
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

%Sales prediction is an important problem that can improve the quality of business strategy for different companies. 
% Antonio - not needed to mention this again in this section. Maybe we can move it to the introduction. ;)
Traditionally, sales prediction problems have been solved using advanced mathematical and machine learning-based methods
% Antonio - why are they 'advanced'?
such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999}, fuzzy systems \cite{Mastorocostas2001}, or mixture of methods \cite{Chang2006715,Meulstee2008,ChiJie2012}.

In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990,KayacanUK10}.
% Antonio - the last reference doesn't exist
However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
Moreover, this kind of methods are based on using historical data to make time series. However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data \cite{ChingChin2010}, 
and only pre-sales data are available \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale. 
% Antonio - We should rewrite this, since a similar sentence was a weak asseveration in previous paper. The proposed methodology also uses historical data to infer the print-run of new books, so, why is this a problem for Time Series and it is useful for the proposed methods? :/

Not only the lack of historical data makes this a complex problem, but also the fact that several `external' variables (seasonality, promotions, or fashions) might influence predictions
\cite{Lapide1999,Thomassey2012,Xia2012,SThomassey2014,ChernWSF15}.
% Antonio - choose just a couple of references to justify this. ;)

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as data clustering and fuzzy neural networks \cite{Chang2009} or extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this line, several authors have applied the ensemble of models for sales forecasting, 
% Antonio - briefly clarify what is an ensemble
as it is done in \cite{ChiJie2012}, where a hybrid forecasting method integrates ensemble empirical model decomposition and extreme learning machine 
% Antonio - learning machine or machine learning?
% Anyway, what does it mean?
to develop an effective forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach for better handling of seasonal changes and fluctuations in consumer demands, whereas Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller and an artificial neural network for sales forecasting in printed circuit board industry.

Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.
% Antonio - comment this last paper

Ching et al. \cite{ChingChin2010} used a decision-support system to classify new 
products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
that products in the same class would follow a similar sales pattern. 
In any case, the proposed system can not deal with qualitative data related to the products. 
In this paper, several classification-based approaches have been implemented and tested, also considering categorical data.

%Finally, in those problems where historical data are available, authors have 
%proposed to apply classical time series forecasting methods.
% Antonio - we said previously more or less that Time Series Prediction is not recommended

In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
to forecast the future sales of a printed circuit board is proposed.
% Antonio - compare it with our work
Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
Similar researches took advantage of the information published on specialized 
blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales. Therefore, different sales patterns have been observed by analysing books in series, i.e. the first book published takes the longest period to achieve every single sales scale, while the second book takes the second longest period, and so on.
In these cases, sales forecasting problems can be carried out thanks to a big 
amount of online reviews and historical data.
% Antonio - compare these works and findings with our current work

This paper continues our previous work on the prediction of sales of a new product for which no historical data are available, and where the classical forecasting methods based on time-series are not adequate \cite{Castillo2016books}. In that paper the main factors influencing sales where 
analyzed in order to create a tool, based on several regression methods, that the publisher can use to decide how many books should be printed.

However, in this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
% TODO: complete this paragraph.
% Antonio - say why we continue the previous work (what wer the flaws), how are we continuing it, wat we expect to improve, the objective contribution, etc
